Hierarchical time series forecasting in Emergency Medical Services

### 2022-11-16 manuscript/main.tex
Now compiling again

\begin{keyword}
    forecasting \sep healthcare \sep emergency services \sep forecast
reconciliation \sep hierarchical time series \sep ambulance demand \sep 
    attended incidents
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, breakable, enhanced, frame hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

We are interested in generating forecasts to inform the planning horizon
of \(ph= 42\) days, required by planners in the ambulance services
trust. The forecast horizon in this study is \(fh = 2 \times ph\) days
ahead (2*42 days planning horizon). This is because the planning is
generally freezed for \(ph\) days and considering a forecast horizon of
\(ph\) days might not be helpful for planning. While forecasts are
generated for \(2 \times ph\) days ahead, performance evaluation is only
assessed based on the last \(ph\) days and not the \(2 \times ph\) days.
The forecasts are produced for the holdout of 365 days using time series
cross-validation \citep{hyndman2021forecasting}.

@@

\includegraphics{/Users/bahmanrostami-tabar/Documents/1-research/1-research_papers/Work with Rob Hyndman/forecasting-emergency-medcine/img/group.png}

@@

\caption{\label{fig-hierarchy}The hierarchical and grouped structure of
attended incidents (ambulance demand)}

@@

In addition to displaying the trend and seasonality features, we also
visualize few time series at various levels of the aggregation. Figure
Figure~\ref{fig-dataviz} reveals different information such as trend,
seasonality and noise. For example, some series depict seasonality and
trend, whereas some other series report low volume of attended incidents
and entropy, making them more volatile and difficult to forecast. At the
level on nature of incidents combined with categories of other levels,
there are many series that contain zeros with low counts. As such, the
data set represents a diverse set of daily time series patterns.

@@

\begin{minipage}[t]{0.49\linewidth}

\includegraphics{main_files/figure-pdf/fig-dataviz-1.pdf}

@@

\subcaption{\label{fig-dataviz-1}Whole country}
\end{minipage}%
%
\begin{minipage}[t]{0.02\linewidth}

\end{minipage}%
%
\begin{minipage}[t]{0.49\linewidth}

\includegraphics{main_files/figure-pdf/fig-dataviz-2.pdf}

\subcaption{\label{fig-dataviz-2}By control area}
\end{minipage}%
\newline
\begin{minipage}[t]{0.49\linewidth}

\includegraphics{main_files/figure-pdf/fig-dataviz-3.pdf}

\subcaption{\label{fig-dataviz-3}By health board and control area}
\end{minipage}%
%
\begin{minipage}[t]{0.02\linewidth}

\end{minipage}%
%
\begin{minipage}[t]{0.49\linewidth}

\includegraphics{main_files/figure-pdf/fig-dataviz-4.pdf}

\subcaption{\label{fig-dataviz-4}By health board and priority}
\end{minipage}%
\newline
\begin{minipage}[t]{\linewidth}

\includegraphics{main_files/figure-pdf/fig-dataviz-5.pdf}

\subcaption{\label{fig-dataviz-5}By nature of incident and health board}
\end{minipage}%

\caption{\label{fig-dataviz}Time series of attended incidents at various
levels.}

@@

where \(F^f_j(x)\) is the forecasted Cumulative Density Function (CDF)
of period \(j\) and 𝐹\(F^0_j(x)\) is the true CDF of period \(j\).

@@

>>>>

\begin{keyword}
    forecasting \sep healthcare \sep emergency services \sep forecast
reconciliation \sep hierarchical time series \sep ambulance demand \sep 
    attended incidents
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, boxrule=0pt, frame hidden, breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

We are interested in generating forecasts to inform the planning horizon
of \(ph= 42\) days, required by planners in the ambulance services
trust. The forecast horizon in this study is \(fh = 2 \times ph\) days
ahead (2*42 days planning horizon). This is because the planning is
generally frozen for \(ph\) days and considering a forecast horizon of
\(ph\) days might not be helpful for planning. While forecasts are
generated for \(2 \times ph\) days ahead, performance evaluation is only
assessed based on the last \(ph\) days and not the \(2 \times ph\) days.
The forecasts are produced for the holdout of 365 days using time series
cross-validation \citep{hyndman2021forecasting}.

@@

\includegraphics{../img/group.png}

@@

\caption{\label{fig-hierarchy}The hierarchical and grouped structure of
attended incidents (ambulance demand).}

@@

In addition to displaying the trend and seasonality features, we also
visualize few time series at various levels of the aggregation. Figure
Figure~\ref{fig-dataviz2} reveals different information such as trend,
seasonality and noise. For example, some series depict seasonality and
trend, whereas some other series report low volume of attended incidents
and entropy, making them more volatile and difficult to forecast. At the
level on nature of incidents combined with categories of other levels,
there are many series that contain zeros with low counts. As such, the
data set represents a diverse set of daily time series patterns.

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{main_files/figure-pdf/fig-dataviz2-1.pdf}

@@

\caption{\label{fig-dataviz2}Time series of attended incidents at
various levels.}

@@

where \(F^f_j(x)\) is the forecasted Cumulative Density Function (CDF)
of period \(j\) and \(F^0_j(x)\) is the true CDF of period \(j\).

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{main_files/figure-pdf/fig-accuracy-1.pdf}

\caption{\label{fig-accuracy}Average accuracy by week for 12 weeks. CRPS
is relative to a naive ECDF. MASE and MSSE are relative to the
corresponding values for the training set.}
